Well-quasi-orderings on word languages

### 2024-08-19 src/introduction.tex
tests and all

@@

\subparagraph{Contribution} 
\AP
In this paper, we focus on words over a finite
alphabet $\Sigma$, and characterize subsets $L \subseteq \Sigma^*$ that are
\kl{well-quasi-ordered} by the \kl{prefix relation}, the \kl{suffix relation},
and the \kl{infix relation}. Let us remark that these word orderings are all
\intro{well-founded}, i.e., they do not contain infinite \intro{decreasing
sequences} $\seqof{x_n}$ such that $x_{n+1} \prec x_n$ for all $n \in \Nat$.
Let us recall that the key difference between \kl{well-quasi-orderings} and the
maybe more usual notion of well-founded orderings is that the latter allows the
existence of infinite \intro{antichains}, that is, sets of pairwise
incomparable elements. In fact, a set $X$ is \kl{well-quasi-ordered} if and
only if it is \kl{well-founded} and does not contain infinite \kl{antichains}
\cite{KRU72}.  As a consequence, our study focuses on detecting infinite
\kl{antichains} in languages $L \subseteq \Sigma^*$.

>>>>

\begin{figure}
    \centering
    \includestandalone{src/prefix-embedding-standalone}

    \includestandalone{src/infix-embedding-standalone}

    \includestandalone{src/subword-embedding-standalone}
    \caption{A simple representation of the \kl{subword relation},
        \kl{prefix relation},
        and \kl{infix relation},
        on the alphabet $\set{a,b}$ for words of
        length at most $3$.}
    \label{word-embeddings:fig}
\end{figure}

@@

\subparagraph{Contribution} \AP In this paper, we focus on words over a finite
alphabet $\Sigma$, and characterize subsets $L \subseteq \Sigma^*$ that are
\kl{well-quasi-ordered} by the \kl{prefix relation}, the \kl{suffix relation},
and the \kl{infix relation}. Let us remark that these word orderings are all
\intro{well-founded}, i.e., they do not contain infinite \intro{decreasing
sequences} $\seqof{x_n}$ such that $x_{n+1} \prec x_n$ for all $n \in \Nat$.
Let us recall that the key difference between \kl{well-quasi-orderings} and the
maybe more usual notion of well-founded orderings is that the latter allows the
existence of infinite \intro{antichains}, that is, sets of pairwise
incomparable elements. In fact, a set $X$ is \kl{well-quasi-ordered} if and
only if it is \kl{well-founded} and does not contain infinite \kl{antichains}
\cite{KRU72}.  As a consequence, our study focuses on detecting infinite
\kl{antichains} in languages $L \subseteq \Sigma^*$. Remark that for the
relations we consider (including the \kl{subword relation}), the set of all
words of a fixed size $k$ is always an \kl{antichain}, and there are therefore
no bound on the maximal length of an antichain.

### 2024-08-19 src/prefixes.tex
tests and all

@@

>>>>

\begin{figure}
    \centering
    \includestandalone{src/antichain-branch-standalone}
    \caption{An \kl{antichain branch} for the language $a^* b$,
        represented in the \kl{tree of prefixes} over the alphabet $\set{a,b}$.
        The branch is represented with dashed lines in turquoise, and the
        \kl{antichain} is represented in dotted lines in blood-red.
    }
    \label{antichain-branch:fig}
\end{figure}

@@

\begin{figure}
    \centering
    TODO.
    \caption{Illustrating the construction of 
        \cref{prefixes:thm} consisting in taking the words
        that lead to prefix-incomparable elements in $S$,
        and then the upwards closure of the maximal such elements.
    }
    \label{prefixes-theorem:fig}
\end{figure}
